Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-07 ms.tex
more Allan variance plots now across cooldowns

>>>>

\clearpage
\subsection{Noise floor}

Allan variance plots indicate that there is a noise floor across detectors of about 50-60 ppm as shown in Figure \ref{fig:allanVarianceAZ04AZ05}.

\begin{figure*}
{\gridline{\fig{allan_var_removelinear_True_azlab05baseline.pdf}{0.48\textwidth}{AZLab05 Allan variance}
\fig{allan_var_removelinear_True_azlab06lamp_warm.pdf}{0.48\textwidth}{AZLab06 Allan variance}}}
\caption{Allan variance across two detectors in the AZ Lab stability tests.}\label{fig:allanVarianceAZ04AZ05}
\end{figure*}
